\documentclass[a4paper,9pt,fleqn]{article}

\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{listings}
\usepackage{alltt}
\usepackage{pgf}
\usepackage{hyperref}
\setlength{\parindent}{0mm}
\setlength{\itemsep}{0ex}
\setlength{\parskip}{2ex}
\setlength{\parsep}{2ex}
\setlength{\partopsep}{0ex}
\setlength{\topsep}{0ex}

\newenvironment{outp}{\fontfamily{pcr}\selectfont}{\courier}

\lstset{
	aboveskip=5mm,
	belowskip=5mm,
	xleftmargin=5mm,
	language=,
	basicstyle=\scriptsize\outp,
	tabsize=2
}


\title{
{\bf Report}\\
\vspace{0.2cm}
%
Home Assignment, CCOM38\\
\vspace{1cm}
%
{
\large
Dennis Bennhage,	bennhage@student.chalmers.se \\
Hampus Lidin,	lidin@student.chalmers.se
}
\\
\vspace{10cm}
%
May 19th, 2015
}

\date{}

\begin{document}

\maketitle

\newpage

\begin{enumerate}[{Task} 1]
	\item :
	\begin{enumerate}[a)]
		\item 
		When running the {\outp ipconfig} command, you get all the
		information about the different interfaces at the host computer. Running the
		command in the Chalmers network, we get the following information
		about the WLAN interface:
			
\begin{lstlisting}
> ifconfig

<output omitted>

Wireless LAN adapter Wireless Network Connection:

   Connection-specific DNS Suffix  . : eduroam.chalmers.se
   Link-local IPv6 Address . . . . . : fe80::6046:472a:63f5:468e%11
   IPv4 Address. . . . . . . . . . . : 129.16.187.2
	 Subnet Mask . . . . . . . . . . . : 255.255.240.0
   Default Gateway . . . . . . . . . : 129.16.176.1

<output omitted>
\end{lstlisting}

		The {\outp IPv4 Address} field shows information about the IPv4 configuration for that
		interface. The unicast IP-address for the local network is then {\outp 129.16.187.2/20},
		with the broadcast address {\outp 129.16.176.1/20}. %However, the
		%IP-address is within the private address space, so the router has to
		%convert it into a globally unique IP-address using {\it Network Address
		%Translation} (NAT). This address is provided to the router by the {\it Internet
		%Service Provider} (ISP), and all traffic in the local network going out
		%from the router will then use this address to communicate through the
		%Internet.
    \\
		\item 
		The hostname can be found using the {\outp nslookup} command on the IP-address
		obtained in the previous task:

\begin{lstlisting}
> nslookup 129.16.187.2

Server:		res1.chalmers.se
Address:	129.16.1.53

Name:		dhcp-187002.eduroam.chalmers.se
Address:	129.16.187.2
\end{lstlisting}

		This tells us that the hostname for the IP-address {\outp 129.16.1.53} is
		{\outp dhcp-187002.eduroam.chalmers.se}, and was given by the name server
		{\outp res1.chalmers.se}.
	\end{enumerate}

	\item :
	\begin{enumerate}[a)]
		\item 
		When using {\outp tracert} for the website {\outp www.uio.no}, we get the following
		results:
		
\newpage

\begin{lstlisting}
Tracing route to www.uio.no [129.240.8.200]
over a maximum of 30 hops:

  1    <1 ms    <1 ms    <1 ms  3.home [192.168.1.1] 
  2     *        *        *     Request timed out.
  3   296 ms   419 ms   354 ms  10.66.130.65 
  4   390 ms   408 ms   412 ms  172.18.4.78 
  5   405 ms   409 ms   409 ms  172.18.72.82 
  6   406 ms   333 ms   280 ms  172.18.8.105 
  7    98 ms    96 ms    98 ms  10.66.54.133 
  8   272 ms   414 ms   406 ms  sejar0001-rc2.ip-only.net [213.132.96.193] 
  9   620 ms   408 ms   419 ms  sejar0001-rc5.ip-only.net [62.109.44.158] 
 10   419 ms   409 ms   613 ms  62.109.44.214 
 11   120 ms    55 ms    55 ms  oslo-gw1.uninett.no [193.156.90.1] 
 12   228 ms    81 ms    52 ms  uio-gw8.uio.no [128.39.65.18] 
 13   111 ms   111 ms    97 ms  mrom-gw2.uio.no [129.240.25.18] 
 14    55 ms    66 ms    56 ms  www.uio.no [129.240.8.200] 

Trace complete.
\end{lstlisting}

		The route stretches from a home network to the University of Oslo. The first hop
		is the source location that {\outp tracert} was issued. At the second hop,
		we can see that the intermediate device didn't respond, so the request timed out.
		The device has likely blocked any incoming {\outp tracert} requests, which is rather
		common to do, to prevent possible {\it denial-of-service} (DoS) attacks. The high
		delays in hops 3 through 6 could be because of higher prioritized traffic being routed
		first, leaving lower prioritized traffic to wait in queue. At hop 7 the delays deminishes.
		In the next three hops, we can see another increase in packet delays. The host name
		{\outp sejar0001-rc2.ip-only.net} belongs to a company in the city of Stockholm. At
		hops 11 and 12, the route has stretched down to Kastrup in Denmark, and at hops 13
		and 14 the final portion of the route has been laid out towards the web server.
		\\
		\item 
		{\outp traceroute}, as the name suggests, traces the route of an IP-packet over
		the Internet. It is usually implemented using the {\it User Datagram Protocol} (UDP),
		to transport the packet from the host computer to a specified destination.
		UDP maintains the route for all packets that it sends, which is essential in order for
		{\outp traceroute} to work.
		\\ \\
		{\outp traceroute} initially sets the maximum {\outp Time To Live} ({\outp TTL}) value
		to 1 in the IP-header. Then after every three packets it sends, the max {\outp TTL} value
		increments by 1. The first three packets will always stop at the IP-configured interface
		of the host computer first. Therefore after packets immediately have left the host, the
		{\outp TTL} will always be 1 less than the max {\outp TTL}. When the first router on the
		route then receives the first packet, it will decrement the {\outp TTL} value by 1, resulting
		in a value of 0. This means that the packet can not be forwarded any further and an
		{\it Internet Control Message Protocol} (ICMP) message is generated. This message goes all
		the way back to the source. In the mean time, {\outp traceroute} started counting the time
		from when the packet was sent, and when the ICMP reply for that packet arrives, it stops the
		timer. The same scenario occurs for the next two packets. When the ICMP reply for
		the third packet arrives, {\outp traceroute} increments the max {\outp TTL} to 3. Then when the
		next heap of three packets packet gets sent to the first router, the router decrements
		{\outp TTL} to 1 and the packet is forwarded to the next router. That router then does the
		same thing and generates an ICMP message (since {\outp TTL} now became 0) that goes back
		to the host. This is repeated until the max {\outp TTL} is large enough to reach the destination.
		This way we can put together a table of three roundtrip times for each node on the route.
	\end{enumerate}

	\item :
	\begin{enumerate}[a)]
		\item 
		The TCP/IP model has 4 layers, going from top to bottom; {\it Application Layer},
		{\it Transport Layer}, {\it Internet Layer} and {\it Link Layer}. When applications
		in the application layer want to send data across the Internet, it has to make use of
		several protocols in order for the data to successfully arrive at the
		destination. Each layer has its own protocols and responsibilities, that
		are transparent to the other layers. For example, the Application Layer can
		use {\it HyperText Transfer Protocol} (HTTP) to send data, but how the data
		is actually sent and how the other protocols work in the other layers, is
		ignored by HTTP. When HTTP wants to send a message to a remote host, it
		passes its data to the layer below, the Transport Layer. TCP is often used
		to make a data transfer for HTTP. TCP breaks up the data into the {\it Protocol
		Data Unit} (PDU) called {\it segment}, where every segment gets its own header. This
		process is called segmentation.
		\\ \\
		TCP makes sure that the data is sent across a network in a reliable fashion.
		How the segments will travel across the network (or any network), is up to the next
		layer, the Internet Layer. Here IP is used to address every IP-enabled end-point in
		the network with a unique IP-address. IP encapsulates the segment into the
		Internet Layer PDU called {\it packet}, also by adding a header with the essential
		information about the data and transfer. How the packet is transferred between to
		directly connected devices in the network is up to the Link Layer. The Link Layer's
		responsibility lies in making sure that the data is sent across a link
		between two devices. The packet gets a header and a trailer in an
		encapsulation called {\it frame}. The frame can be sent on any medium, as long
		as there is protocols for it to handle the process. When a frame has been sent
		across the medium, a new header and trailer is added for the next link
		transfer.
		\\ \\
		When the first frame arrives at the destination, decapsulation begins.
		The frame header and trailer are removed and the packet is revealed to the
		Internet Layer. After checking that the right packet has arrived, it
		removes its header as well and sends it to the Transport Layer. The
		Transport Layer also checks the validity of the segment, then decapsulate
		it and passes it on to the right application. The application then checks
		the message and does whatever it wants with the data.
		\\
		\item 
		A {\it Peer-to-Peer-Protocol} (P2PP) is a protocol that establishes communication
		between two entities, or hosts, in the layer that it operates in. P2PPs are
		only concerned about the responsibilities of their own layers, and do not bother
		about the implementation of other layers and protocols. For example, TCP
		establishes a connection over a network, by performing the {\it three-way handshake}
		between two hosts. The two hosts operate in a similar way as each other, but none
		of them care about how the data is being transferred across the network. They only
		care about the reliability and verification of the transfer, while delegating
		the routing, media access control and other things to lower layers.
	\end{enumerate}

\item :
	\begin{enumerate}[a)]
		\item
		Blablabla.

\begin{lstlisting}
www.chalmers.se:

	HEAD / HTTP/1.0

	HTTP/1.1 401 Unauthorized
	Content-Length: 16
	Content-Type: text/html; charset=utf-8
	Server: Microsoft-IIS/7.5
	SPRequestGuid: 1b34a246-0f4b-4010-9e90-6fd42daab1e4
	X-SharePointHealthScore: 0
	WWW-Authenticate: NTLM
	X-Powered-By: ASP.NET
	MicrosoftSharePointTeamServices: 14.0.0.7102
	X-MS-InvokeApp: 1; RequireReadOnly
	Date: Mon, 18 May 2015 08:20:33 GMT
	Connection: close
\end{lstlisting}	

		The type of web server {\outp www.chalmers.se} is using is {\outp Microsoft-IIS/7.5}.
		We get the response {\outp 401 Unauthorized}, which means that we do not have access
		to URL resources without providing user authentication (log in somewhere with
		a username and a password). The authentication protocol in this case, which
		is specified in the {\outp WWW-Authenticate} field of the HTTP header, is {\outp NTLM}.
		\\ \\
		Content-Length is the size of the content that is being sent, in octets(bytes).
		Content-Type indicates what type of media is being sent.
		SPRequestGuid contains diagnostic information about server problems.
		X-SharePointHealthScore is a number between 0 and 10 where 0 indicates low server load and 10 indicates high server load.
		X-Powered-By specifies which technology is used to support the web application.
		MicrosoftSharePointTeamServices indicates which version of Microsoft SharePoint is installed.
		X-MS-InvokeApp specifies if the application wants to use DirectInvoke, which lets a user open for example a PDF without first saving it to their computer. 
		RequiredReadOnly means that it opens in Read-Only mode.

\begin{lstlisting}
	www.tue.nl:

	HEAD / HTTP/1.0

	HTTP/1.1 301 Moved Permanently
	Date: Mon, 18 May 2015 08:24:17 GMT
	Server: Apache/2.2.22 (Ubuntu)
	X-Powered-By: PHP/5.3.10-1ubuntu3.18
	Location: http://www.tue.nl/
	Vary: Accept-Encoding
	Content-Type: text/html


	Connection closed by foreign host.
\end{lstlisting}

		{\outp www.tue.nl} is using the web server type {\outp Apache/2.2.22 (Ubuntu)}.
		301 Move Permanently means that the resource we are requesting has been redirected
		to a new URL. The new URL is specified in the Location field. In this case www.tue.nl
		is redirecting to http://www.tue.nl/. The Vary field specifies which fields of the
		request header to take into account when trying to find the right object in the cache.
		\\
		\item 
		Blablabla.

\begin{lstlisting}
www.chalmers.se:

	HEAD / HTTP/1.1

	HTTP/1.1 400 Bad Request
	Content-Length: 334
	Content-Type: text/html; charset=us-ascii
	Server: Microsoft-HTTPAPI/2.0
	Date: Mon, 18 May 2015 09:15:38 GMT
	Connection: close

	www.tue.nl:

	HEAD / HTTP/1.1

	HTTP/1.1 400 Bad Request
	Date: Mon, 18 May 2015 09:16:38 GMT
	Server: Apache/2.2.22 (Ubuntu)
	Vary: Accept-Encoding
	Connection: close
	Content-Type: text/html; charset=iso-8859-1
\end{lstlisting}
		
		Blablabla.
		\\
		\item 
		Blablabla.

\begin{lstlisting}
www.chalmers.se:

	HEAD / HTTP/1.1
	Host: www.chalmers.se

	HTTP/1.1 302 Redirect
	Content-Length: 164
	Content-Type: text/html; charset=UTF-8
	Location: http://www.chalmers.se/Pages/default.aspx
	Server: Microsoft-IIS/7.5
	SPRequestGuid: f25d9db4-5345-4c46-b7fc-292c52258273
	X-SharePointHealthScore: 0
	X-Powered-By: ASP.NET
	MicrosoftSharePointTeamServices: 14.0.0.7102
	X-MS-InvokeApp: 1; RequireReadOnly
	Date: Mon, 18 May 2015 09:27:28 GMT

www.tue.nl:

	HEAD / HTTP/1.1
	Host: www.tue.nl

	HTTP/1.1 200 OK
	Date: Mon, 18 May 2015 09:28:56 GMT
	Server: Apache/2.2.22 (Ubuntu)
	X-Powered-By: PHP/5.3.10-1ubuntu3.18
	Set-Cookie: fe_typo_user=e4577ddec4a01568b6eefae39b0dcf4b; path=/
	Expires: Mon, 18 May 2015 10:21:29 GMT
	Cache-Control: max-age=3144
	Vary: Accept-Encoding
	Content-Type: text/html; charset=utf-8

	Connection closed by foreign host.
\end{lstlisting}

		In an HTTP 1.1 request you have to specify the name of the host of the resource
		you are requesting. You can also specify a port number, but we did not do that
		since it defaults to 80 if you do not specify one. If we do not include a host
		name in the request, the server responds with 400 Bad Request, as we saw in 4b.
		\\
		\\
		Say for example that we are hosting several different websites on a single machine.
		They all share an IP address. To be able to send the request to the correct
		website, we need to specify a host name. This is what the host header field is used
		for; differentiating between multiple hosts on the same IP.

	\end{enumerate}

	\item :
	\begin{enumerate}[a)]
		\item 
		{\it Cookie-files}, or {\it cookies}, are web files that are stored in the web browser.
		When browsing a website, a pop-up window might appear asking the user if it wants to
		enable cookies in the current web browser. If the user accepts, the website will keep
		track of what the user do on the website and then tells the browser to store this
		information as cookies on the computer.
		\\
		\\
		When using the latest version of {\it Firefox} web browser, you can view what cookies
		are stored on your computer. By going to the {\it Privacy} tab in {\it Options} and
		clicking {\it remove individual cookies}, you can see all cookies in a list. As an example,
		the following text shows the contents of a cookie after visiting Amazon's website:

\newpage

\begin{lstlisting}[basicstyle=\small]
         Name:	skin
      Content:	noskin
       Domain:	.amazon.com
         Path:	/
     Send For:	Any type of connection
      Expires:	At end of session
\end{lstlisting}

		Here we see a cookie named {\outp skin} that was stored while browsing
		{\outp www.amazon.com}, with the content {\outp noskin}. The cookie also
		contains information about the domain, the {\it Uniform Resource Indentificator} (URI) path
		for the cookie and when the cookie expires.
		\\ 
		\item 
		Using {\outp telnet}, we can find out about the cookie header-line:

\begin{lstlisting}
> telnet www.amazon.com 80

HEAD / HTTP/1.1
Host: www.amazon.com


Response:

	<output omitted>
	
	Set-Cookie: skin=noskin; path=/; domain=.amazon.com
	
	<output omitted>
\end{lstlisting}

		To find out more about the syntax of the header-line, we have to consult the
		{\it Request For Comments} (RFC) document for cookies. RFC 6265 specifies 
		the latest standards for cookies. The header contains three name-value pairs.
		The first one specifies the name of the cookie and the content it carries.
		In this case the name of the cookie is {\outp skin}, with the content {\outp noskin}.
		{\outp path} specifies the URI for the cookie, which has a value of {\outp \textbackslash}.
		This tells the host to store the default-value in the cookie. The last field is the
		{\outp domain}. Here we see that the server tells us that {\outp amazon.com} is
		the domain for the cookie (leading ``.'' are omitted).

	\end{enumerate}

	\item :
	\begin{enumerate}[a)]
		\item 
		The {\outp nslookup} command can be used to find information about the DNS servers of a domain.
		We will use {\outp utoronto.ca} (University of Toronto) for this task.  Here are the results of
		our {\outp nslookup} for {\outp utoronto.ca}:

\begin{lstlisting}
> nslookup -type=mx utoronto.ca
	
Server:  res1.chalmers.se
Address:  129.16.1.53

Non-authoritative answer:
utoronto.ca     MX preference = 10, mail exchanger = k.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = d.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = b.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = c.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = g.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = a.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = l.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = e.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = f.mx.utoronto.ca
utoronto.ca     MX preference = 10, mail exchanger = j.mx.utoronto.ca

utoronto.ca     nameserver = bay.cs.utoronto.ca
utoronto.ca     nameserver = ns2.utoronto.ca
utoronto.ca     nameserver = ns1.utoronto.ca
utoronto.ca     nameserver = ns7.utoronto.ca
bay.cs.utoronto.ca      internet address = 128.100.1.1
ns1.utoronto.ca internet address = 128.100.100.129
ns2.utoronto.ca internet address = 128.100.72.168
ns7.utoronto.ca internet address = 162.243.71.42
\end{lstlisting}

		To find the mail servers we set the type parameter to {\outp MX} (Mail eXchange).
		We find that there are 10 mail servers for {\outp utoronto.ca}, with all of them
		having equal priority (preference = 10). All of them having equal priority
		means that we do not care which of the mail servers we use first. 
		\\ \\
		We also find the DNS servers and their respective IP addresses. 
		\\
		\item
		We use {\outp www.google.com} for this task.

\begin{lstlisting}
> nslookup www.google.com

Server:  	res1.chalmers.se
Address:  	129.16.1.53

Non-authoritative answer:
Name:    	www.google.com
Addresses:  2a00:1450:4010:c02::68
         		74.125.205.106
         		74.125.205.103
         		74.125.205.105
         		74.125.205.99
         		74.125.205.147
         		74.125.205.104
\end{lstlisting}

		We can see that www.google.com has 6 different IP addresses. Multiple IP addresses
		can be used to balance load between web servers. There can be several copies of the
		same web site, each having its own IP address but all using the same DNS servers. The
		first user who sends a request is sent to the first IP address, the second person to
		the second IP address and so on. This reduces the amount of requests to each web server
		and provides redundancy in case a web server should go down.s
		\\ \\
		Multiple IP addresses can also be used to have different IP addresses for different services.
	\end{enumerate}

	\item :
	\begin{enumerate}[a)]
		\item 
		TCP uses {\it timeout} to prevent possible delays in the transfer. If one segment doesn't get
		acknowledged (ACK'ed), it would be bad if the whole transfer had to stall while waiting
		for a reply. Instead it uses a timer to count down a segments maximum {\it Round Trip Time}
		(RTT). When the timer ticks down to zero, the segment is considered lost and a duplicate segment
		is sent. As the transfer proceeds, TCP will calculate new timeouts as it ``learns'' that 
		the segments arrives either faster or slower. The tighter the timeout window is, the faster
		TCP can discover that a segment is lost.   
		\\
		\item 
		When calculating the timeout window, TCP makes use of the {\it recorded} RTTs and the
		{\it estimated} RTTs. We could just simply calculate the window by adding a little more
		time to the recorded RTT, but that would lead to big variations and unstable transfer
		flow. Instead we only count for a portion of the latest RTT sample and add it to the
		complement portion of the previous calculation. This is what's called the estimated
		RTT, and unlike the recorded RTT, it's less prone to fluctuation.
		\\ \\
		To actually determine a value for the timeout window, we need to calculate the deviation
		of the sample RTT from the estimated RTT. Big fluctuations between these should affect
		the deviation value more, and contrary small fluctuations should affect it less. By adding
		an appropriate multiple of this deviation to the estimated RTT, we get an even calculation
		of the timeout value, that adapts fairly quickly to data rate changes.  
	\end{enumerate}
\end{enumerate}

\end{document}